Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Slightly curtail related work

% Pochoir
\citet{Tang:2011:SPAA} define a specification language for writing
stencils embedded in C++ (with Cilk~\citep{blumofe1996cilk} extensions) that
are then compiled
into fast parallel programs based on trapezoidal decompositions with
hyperspace cuts. The Pochoir specification language is used for
describing the kernel, boundary conditions and shape of the
stencil. Programs are first compiled in C++ with a template library
that checks whether the annotations are used correctly, and then a
Pochoir preprocessor may be applied to generate the high-performance
parallel versions using Cilk.  Pochoir
is aimed primarily at assisting programmers who may be reluctant to
implement the high-performance tricky cache-oblivious
``hypertrapezoidal'' algorithms for stencils. 
%that are significantly faster than the typical looping implementations
%of stencil computations.
Like much of the related work, the main goal 
is optimisation rather than verifying program correctness.

>>>>

% Pochoir
\citet{Tang:2011:SPAA} define a specification language for writing stencils
embedded in C++ (with Cilk~\citep{blumofe1996cilk} extensions) that are then
compiled into parallel programs based on trapezoidal decompositions with
hyperspace cuts. The Pochoir specifications are used for describing the kernel,
boundary conditions, and shape of the stencil. Pochoir is aimed at programmers
reluctant to implement the high-performance cache-oblivious
``hypertrapezoidal'' algorithms for stencils.  Like much of the related work,
the goal is optimisation rather than verifying program correctness.
